Language-Based Security for Low-Level MPC

### 2024-05-13 ppdp24/examples.tex
checkpoint

To capture this convention, which is used in many other protocols, we
introduce a new naming convention for ``global view'' elements
$\macgv{\mesg{w}}$, which denote the summed value of
$\elab{\mesg{w}}{1}$ and $\elab{\mesg{w}}{2}$ in a protocol
run. This concept integrates program distributions in the
usual manner, as the probability of the outcome of summation
of two variables in the distribution.
\begin{definition}
  For all $\mesg{w}$ define:
  $$\pmf(\macgv{\mesg{w}} = v) \defeq \sum_{\sigma \in A} \pmf(\sigma)$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\mesg{w}} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\mesg{w}}{1}) + \store(\elab{\mesg{w}}{2})} = v \}$.
\end{definition}

@@

A field value $v$ is secret shared among 2 clientz in BDOZ as follows.
Each client $\cid$ gets a pair of the form $(v_\cid,m_\cid)$, where
$v_\cid$ is a secret share of $v$, i.e., $v = \fcod{v_1 \fplus v_2}$.
Further, field values $m_\cid$ are MACs of $v_\cid$ that are authenticated
by the other client's key. In particular, $m_\cid = k + (k_\Delta *
v_\cid)$ where \emph{keys} $k$ and $k_\Delta$ are known only to $\cid'
\ne \cid$ and $k_\Delta$. Further, there is a unique \emph{local key}
$k$ for each shared value, while the \emph{global key} $k_\Delta$ is
common to all MACs authenticated by $\cid'$. By extending certain
field operations to these MACed values, a semi-homorphic encryption
scheme is obtained that is adequate to compute Beaver Triples. For
example, if local keys $k_1$ and $k_2$ authenticate $\macv_1$ and
$\macv_2$, then $k_1 \fplus k_2$ authenticates $\macv_1 \macplus
\macv_2$, where $\macplus$ is addition extended to MACed
values. Semantics for summation of MACed shares, and multipication of
shares and plain field values, are given in Figure \ref{fig-bdoz}.
For more details the reader is referred to \cite{XXX}. We note
that while we restrict values $v$, $m$, and $k$ to the same
field in this presentation for simplicity, in general $m$ and
$k$ can be in extensions of $\mathbb{Z}_p$.

>>>>

To capture this convention, which is used in many other protocols, we
introduce a new naming convention for ``global view'' elements
$\macgv{\mesg{w}}$, which denote the summed value of
$\elab{\mesg{w}}{1}$ and $\elab{\mesg{w}}{2}$ in a protocol
run. This concept integrates program distributions in the
usual manner, as the probability of the outcome of summation
of two variables in the distribution.
\begin{definition}
  For all $\mesg{w}$ define:
  $$\pmf(\macgv{\mesg{w}} = v) \defeq \sum_{\sigma \in A} \pmf(\sigma)$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\mesg{w}} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A$ is:
  $$\{ \store \in \mems(\{ \elab{\mesg{w}}{1},\elab{\mesg{w}}{2} \} ) \mid
      \fcod{\store(\elab{\mesg{w}}{1}) + \store(\elab{\mesg{w}}{2})} = v \}$$
\end{definition}

@@

A field value $v$ is secret shared among 2 client in BDOZ in
the same manner as in GMW.
Each client $\cid$ gets a pair of the form $(v_\cid,m_\cid)$, where
$v_\cid$ is a secret share of $v$, i.e., $v = \fcod{v_1 \fplus v_2}$.
Further, field values $m_\cid$ are MACs of $v_\cid$ that are authenticated
by the other client's key. In particular, $m_\cid = k + (k_\Delta *
v_\cid)$ where \emph{keys} $k$ and $k_\Delta$ are known only to $\cid'
\ne \cid$ and $k_\Delta$. Further, there is a unique \emph{local key}
$k$ for each shared value, while the \emph{global key} $k_\Delta$ is
common to all MACs authenticated by $\cid'$. By extending certain
field operations to these MACed values, a semi-homorphic encryption
scheme is obtained that is adequate to compute Beaver Triples. For
example, if local keys $k_1$ and $k_2$ authenticate $\macv_1$ and
$\macv_2$, then $k_1 \fplus k_2$ authenticates $\macv_1 \macplus
\macv_2$, where $\macplus$ is addition extended to MACed
values. Semantics for summation of MACed shares, and multipication of
shares and plain field values, are given in Figure \ref{fig-bdoz}.
For more details the reader is referred to \cite{XXX}. We note
that while we restrict values $v$, $m$, and $k$ to the same
field in this presentation for simplicity, in general $m$ and
$k$ can be in extensions of $\mathbb{Z}_p$.
